Road Accident Prediction in Time and Space

### 2019-04-22 paper/paper.tex
Paper: Rewrote Choice of an evaluation metric: give more explanations

\subsection{Choice of a metric to evaluate our models}
The chosen metric for the evaluation of the models was the area under the precision-recall curve (area under PR). According to Davis and Goadrich\cite{Davis} this measure is the most representative of how well a model has been trained in the case of data imbalance, particularly compared to the ROC curve which is the commonly used measure. One can intuitively be convinced because in the ROC curve the false positive rate (FPR) is used instead of the precision. The precision refers to the proportion of examples detected as positive which are actually positive, while the FPR refers to the proportion of negative detected as positives. With an imbalanced dataset, the FPR will usually stay very low because the number of negative is high. The precision, by contrast, will usually be quite low since algorithms tuned for data imbalance will usually include many false positives in the examples they detect in order to achieve a correct recall also called true positive rate.

>>>>

\subsection{Choice of an evaluation metric}
Usually, the accuracy is used to evaluate the performance of classification models, but with an imbalance dataset, this measure does not reflect the real predictive power of the model. Indeed, it is usually easy to predict that an example is in the negative class and machine learning models will usually achieve a very good accuracy for the negative class. Since most examples belong to the negative class, the overall accuracy will be very good as well. However, what we are usually interested in, and this is the case in accident prediction, is to correctly detect the positive examples.
Therefore, we used the precision and the recall measures. The precision is the proportion of examples detected as positive which are actually positive and the recall, also called the true positive rate, is the proportion of positive examples which are detected as positive. The false positive rate (FPR) is also usually used in binary classification, it is the proportion of negative examples which are detected as positives. With an imbalance dataset, the FPR will usually stay very low because the number of negative is high, that is why we used the precision instead.
By decreasing the threshold used by the machine learning model to consider an example as positive, we can get a better recall with a worse precision, in order to measure the predictive power of our model independently of the choice of the threshold, we used the area under the precision-recall curve as our main metric.
